Proposal: What is the impact of weather catastrophe frequency and severity on property insurance policy prices, and how can homeowners alleviate financial strain?

### 2023-10-09 proposal/proposal.tex
ran bibtex
modified bib
citations edited

\paragraph{Introduction}
Weather catastrophes, including hurricanes, tornados, wildfires, hail storms, and other extreme weather events, have been increasingly 
prevalent and severe in recent years. These events pose significant risks to homeowners and carry substantial financial implications. 
This research proposal aims to investigate how the frequency and severity of weather catastrophes impact the pricing of property 
insurance policies and to identify strategies that can be developed to mitigate the financial burden on homeowners. Previous studies 
in the field \citep[e.g.,][]{kraehnert2021} have provided valuable insights, and we seek to build upon their findings.

@@

\paragraph{Data}
We will primarily rely on information acquired from reputable sources for our research, particularly the Insurance Information 
Institute (III) \citep{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \citep{aon}, which acts as a trustworthy and up-to-date reference for data 
regarding catastrophic events. This report delivers in-depth insights into the frequency, severity, and financial effects of numerous 
weather-related catastrophes, including hurricanes, wildfires, severe storms, and more. The III gathers information on the frequency 
and severity of catastrophic events, the insured losses incurred, and their effects on the insurance industry, using Aon as one of 
its main references. Data on current trends and patterns in weather catastrophes and their economic effects can be found in Aon's 
2023 report. Additionally, information on insured and uninsured losses, claim histories, and regional effects can all be found in 
this report which are crucial to our analysis. The report includes a variety of factors, such as the frequency of weather disasters, 
their geographic distribution, the financial losses connected to each incident, and the degree to which these losses are insured. 
In addition, the report provides information on demographics, policy coverage specifics, and insurance premiums, enabling us to 
investigate the connection between weather catastrophes and home insurance premiums.

\paragraph{Research Design and Methods}
In order to fully address the research objectives, our research design and methods will take an integrated approach. We will start by 
performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \citep{iii}and Aon's 2023 Weather, 
Climate, and Catastrophe Insight Report\citep{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
and the pricing of property insurance, this analysis will use statistical techniques like regression analysis and correlation studies.

@@

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

>>>>

\paragraph{Introduction}
Weather catastrophes, including hurricanes, tornados, wildfires, hail storms, and other extreme weather events, have been increasingly 
prevalent and severe in recent years. These events pose significant risks to homeowners and carry substantial financial implications. 
This research proposal aims to investigate how the frequency and severity of weather catastrophes impact the pricing of property 
insurance policies and to identify strategies that can be developed to mitigate the financial burden on homeowners. Previous studies 
in the field \cite[e.g.,][]{kraehnert2021} have provided valuable insights, and we seek to build upon their findings.

@@

\paragraph{Data}
We will primarily rely on information acquired from reputable sources for our research, particularly the Insurance Information 
Institute (III) \cite{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \cite{aon}, which acts as a trustworthy and up-to-date reference for data 
regarding catastrophic events. This report delivers in-depth insights into the frequency, severity, and financial effects of numerous 
weather-related catastrophes, including hurricanes, wildfires, severe storms, and more. The III gathers information on the frequency 
and severity of catastrophic events, the insured losses incurred, and their effects on the insurance industry, using Aon as one of 
its main references. Data on current trends and patterns in weather catastrophes and their economic effects can be found in Aon's 
2023 report. Additionally, information on insured and uninsured losses, claim histories, and regional effects can all be found in 
this report which are crucial to our analysis. The report includes a variety of factors, such as the frequency of weather disasters, 
their geographic distribution, the financial losses connected to each incident, and the degree to which these losses are insured. 
In addition, the report provides information on demographics, policy coverage specifics, and insurance premiums, enabling us to 
investigate the connection between weather catastrophes and home insurance premiums.

\paragraph{Research Design and Methods}
In order to fully address the research objectives, our research design and methods will take an integrated approach. We will start by 
performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \cite{iii}and Aon's 2023 Weather, 
Climate, and Catastrophe Insight Report\cite{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
and the pricing of property insurance, this analysis will use statistical techniques like regression analysis and correlation studies.

@@

\bibliography{refs}
\bibliographystyle{chicago}
